Numerical experiment investigating the influence of drag on trajectory patterns of floating macroalgae

### 2021-03-30 thesis_chapter_3.Rmd
figure 1 caption update

```{r map, echo=FALSE, message=FALSE, warning=FALSE, strip.white=TRUE, fig.cap="Figure 1: Map of the study domain and the main features pertaining to transport in the region. In panel A, the map of the entire South African coastline and the main currents presented. The resulting eddies and filaments from the Agulhas retroflection and study area are presented. In panel B, the splitting of the Benguela Jet, eddie features and general flow of the study domain are presented. The release site is represented by a blue star."}

>>>>

```{r map, echo=FALSE, message=FALSE, warning=FALSE, strip.white=TRUE, fig.cap="Figure 1: Map of the study domain and the main features pertaining to transport in the region. In panel A, the map of the entire South African coastline and the main currents is presented. The resulting eddies and filaments from the Agulhas retroflection are indicated, and the position of the study area is drawn in as a black rectangle. Detail of the study area is in panel B. Here the splitting of the Benguela Jet, eddie features, and the general flow of the study domain are presented. The release site of simulated kelp ‘particles’ is represented by a blue star."}
